Formatting Instructions \\for Authors Using \LaTeX{}

### 2016-05-23 doc/paper.tex
topicalization, with pronoun antecedent specified in template
noun data entry - with a productivity-increasing script

Such synthetic parallel corpora can also be viewed as benchmark tasks (need to cite Facebook bAbI).

@@

@@

>>>>

Such synthetic parallel corpora can also be viewed as benchmark tasks (need to cite Facebook bAbI).
This is actually probably more important than you'd think, because looking at IWSLT15, some of the human translations are VERY loose.
So there's another element of noise in the data, and it's one that no amount of downstream machine learning can get rid of.
(Although people have tried corpus evaluation...)

@@

My main point seems to be that nobody makes high quality and quantity parallel corpora JUST for machine translation, and it seems like that's sorely needed for both training and benchmarking.
Even the fanciest new machine learning model is dead in the water if it doesn't have enough data.

@@

This is (probably? ref??) unlike other NLG work in that our emphasis is on surface forms, not the underlying data representation.
